<!--
---
title: "R Markdown Demo"
author: "Anton Antonov"
date: "Saturday, April 25, 2015"
output:
  html_document:
    css: custom.css
    toc: yes
  pdf_document:
    number_sections: yes
    toc: yes
---
-->
<!--
  ioslides_presentation:
    widescreen: yes
-->


# Science, I'm coming for you!

I am so excited to present my breakthrough research in quantum theory. 

## Theoretical basis

Let's imagine a **cat**. Not just any *random cat*, but a decent scientific one!

Like this:

![Chemistry cat][cat]

[cat]: cat2.jpg "Do you love chemistry?"

This cat is 

* fluffy
* ~~black~~ white

Cats and science have been together for a long time, e.g. [Schrödinger's cat](http://en.wikipedia.org/wiki/Schr%C3%B6dinger's_cat).

That's enough for the first page. <sub> No one likes too much text. </sub>

-----

## R to the rescue

We are using `library(knitr)` to make some calculations in R and put them here.

For instance, take the well known `iris` dataset. 
It is a data frame that consists of ```r ncol(iris)``` columns (variables) 
and ```r nrow(iris)``` rows (observations). 

It starts like so:
```{r}
head(iris)
```

I'd like to calculate variable means across groups. Here's the code I use:
```{r, eval=FALSE}
aggregate(subset(iris, select = -Species), iris[, "Species", drop = FALSE], mean)
```

Here's the output I get:
```{r, echo=FALSE}
aggregate(subset(iris, select = -Species), iris[, "Species", drop = FALSE], mean)
```

I can embed plots!
```{r, message=FALSE, fig.height=6, fig.width=8}
library(ggplot2)
ggplot(iris, aes(x = Sepal.Length, y = Sepal.Width, color = Species)) +
  geom_point(size = 4)
```

There's a `cache` option for lengthy computations. 
```{r long_calc, cache=TRUE, echo=FALSE}
sum <- 0
for (i in 1:400) {
  Sys.sleep(0.01)
  sum <- sum + rnorm(1)
}
paste0("Result: ", sum)

```

## Bonus

```{r leaflet}
library(leaflet)
leaflet() %>% 
  addTiles() %>% 
  setView(30.34701, 59.92359, zoom = 16) %>%
  addPopups(30.34701, 59.92359, 'We are here <em>somewhere.</em>')
```

